### 2021-07-05 docs/manuscript/manuscript.tex
Rephrase Author summary

% Please keep the Author Summary between 150 and 200 words
% Use first person. PLOS ONE authors please skip this step.
% Author Summary not valid for PLOS ONE submissions.
\section*{Author summary}
Systems biology is a very fast growing field thanks to the advances in computing and
mathematical modeling of biological systems, and has proven to be a powerful tool that
can help us to understand complex biological processes such as pattern formation in
development. In this article we use an \textit{in silico} approach in order to find and study
the design space of multiple input three node Gene Regulatory Networks that are able
to produce a striped pattern of gene expression.

>>>>

% Please keep the Author Summary between 150 and 200 words
% Use first person. PLOS ONE authors please skip this step.
% Author Summary not valid for PLOS ONE submissions.
\section*{Author summary}
Systems biology is a fast growing field largely powered by advances in
high-performance computing and sophisticated mathematical modeling of
biological systems. Based on these advances, we are now in a position to not
only mechanistically understand but also to accurately predict the behavior of
complex biological processes, including cell differentiation and spatial pattern
formation during embryogenesis. In this article we use an \textit{in silico}
approach to probe the design space of multi-input, three node Gene Regulatory
Networks (GRNs) capable of generating a striped pattern of gene expression in
the context of a simplified 1-D morphogenetic field.
